Asimilación de distintas observaciones

### 2021-01-07 analysis/chapters/experimento_20181122.Rmd
Impacto de las obs?

rad %>% 
  .[sensor == "iasi_metop-b" & 
      channel == 335 & 
      qc == 0 & iuse == 1] %>% 
  .[, date := factor(date)] %>% 
  ggplot(aes(ConvertLongitude(lon), lat)) +
  geom_point(aes(color = tbc)) +
  scale_color_divergent(trans = mesoda::symlog_trans(),
                        guide = guide_colourbar(barheight = 15, barwidth = 1)) +
  geom_mapa() +
  facet_grid(run~date, labeller = labeller(run = c("diagfiles" = "OmB",
                                                   "diagfiles_ana" = "OmA"))) +
  labs(x = NULL, y = NULL, color = NULL) +
  theme_minimal() +

  rad %>% 
  .[sensor == "iasi_metop-b" & 
      channel == 335 & 
      # qc == 0 & 
      iuse == 1] %>% 
  dcast(lon + lat + date ~ run, value.var = c("tbc")) %>% 
  .[, ":="(tbc = diagfiles - diagfiles_ana,
           run = "AmB")] %>% 
  .[, date := factor(date)] %>% 
  ggplot(aes(ConvertLongitude(lon), lat)) +
  geom_point(aes(color = tbc)) +
  scale_color_divergent(guide = guide_colourbar(barheight = 15, barwidth = 1)) +
  geom_mapa() +
  labs(x = NULL, y = NULL, color = NULL) +
  facet_grid(run~date) +
  theme_minimal() +
  plot_layout(ncol = 2, widths = c(0.4, 0.6))
```

>>>>

rad %>% 
  .[sensor == "iasi_metop-b" & 
      channel == 335 & 
      errinv %between% c(0.0000316227, 1000) & 
      qc == 0 & 
      iuse == 1 &
      peakwt %between% c(0.001, 1200)] %>% 
  .[, date := factor(date)] %>% 
  ggplot(aes(ConvertLongitude(lon), lat)) +
  geom_point(aes(color = tbc)) +
  scale_color_divergent(trans = mesoda::symlog_trans(),
                        guide = guide_colourbar(barheight = 15, barwidth = 1)) +
  geom_mapa() +
  facet_grid(run~date, labeller = labeller(run = c("diagfiles" = "OmB",
                                                   "diagfiles_ana" = "OmA"))) +
  labs(x = NULL, y = NULL, color = NULL) +
  theme_minimal() +

  rad %>% 
  .[sensor == "iasi_metop-b" & 
      channel == 335 & 
      errinv %between% c(0.0000316227, 1000) & 
      qc == 0 & 
      iuse == 1 &
      peakwt %between% c(0.001, 1200)] %>% 
  dcast(lon + lat + date ~ run, value.var = c("tbc")) %>% 
  .[, ":="(tbc = diagfiles - diagfiles_ana,
           run = "AmB")] %>% 
  .[, date := factor(date)] %>% 
  ggplot(aes(ConvertLongitude(lon), lat)) +
  geom_point(aes(color = tbc)) +
  scale_color_divergent(guide = guide_colourbar(barheight = 15, barwidth = 1)) +
  geom_mapa() +
  labs(x = NULL, y = NULL, color = NULL) +
  facet_grid(run~date) +
  theme_minimal() +
  plot_layout(ncol = 2, widths = c(0.4, 0.6))
```
```{r}
files <- c(Sys.glob("/home/paola.corrales/datosmunin/EXP/E7/ANA/20181121010000/diagfiles*/asim_*ensmean"), Sys.glob("/home/paola.corrales/datosmunin/EXP/E7/ANA/20181121130000/diagfiles*/asim_*ensmean"))

files <- Sys.glob("/home/paola.corrales/datosmunin/EXP/E7/ANA/20181121130000/diagfiles*/asim_*ensmean")

files <- files[str_detect(files, "conv", negate = TRUE)]

  rad <- read_diag_rad(f, "E7") %>% 
    .[, run := basename(dirname(f))] %>% 
    .[, wavenumber := 1/(299792458/(freq*10000000))] %>% 
    # .[wavenumber %between% c(1367, 1422.25)] %>% 
    satinfo[., on = c("sensor", "channel")]
}) %>% rbindlist()

rad %>% 
  .[run == "diagfiles"] %>% 
  .[errinv %between% c(0.0000316227, 1000) & 
      qc == 0 & 
      iuse == 1 &
      peakwt %between% c(0.001, 1200)] %>% 
  .[, date := factor(date)] %>% 
  ggplot(aes(ConvertLongitude(lon), lat)) +
  geom_point(aes(color = sensor, shape = sensor), size = 0.8) +
  # scale_color_divergent(trans = mesoda::symlog_trans(),
  #                       guide = guide_colourbar(barheight = 15, barwidth = 1)) +
  scale_color_brewer(palette = "Dark2") +
  geom_mapa() +
  # facet_grid(run~date, labeller = labeller(run = c("diagfiles" = "OmB",
  #                                                  "diagfiles_ana" = "OmA"))) +
  labs(x = NULL, y = NULL, color = NULL, shape = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom")

  rad %>% 
  .[sensor == "iasi_metop-b" & 
      channel == 335 & 
      errinv %between% c(0.0000316227, 1000) & 
      qc == 0 & 
      iuse == 1 &
      peakwt %between% c(0.001, 1200)] %>% 
  dcast(lon + lat + date ~ run, value.var = c("tbc")) %>% 
  .[, ":="(tbc = diagfiles - diagfiles_ana,
           run = "AmB")] %>% 
  .[, date := factor(date)] %>% 
  ggplot(aes(ConvertLongitude(lon), lat)) +
  geom_point(aes(color = tbc)) +
  scale_color_divergent(guide = guide_colourbar(barheight = 15, barwidth = 1)) +
  geom_mapa() +
  labs(x = NULL, y = NULL, color = NULL) +
  facet_grid(run~date) +
  theme_minimal() +
  plot_layout(ncol = 2, widths = c(0.4, 0.6))
```
